### 2018-04-19 experiments.tex
wording

Using TSTL's harness for {\tt redis-py}, both {\tt redis-py} and Redis
itself can be tested; unfortunately, generating standalone
high-coverage regression tests for {\tt redis-py} and Redis using TSTL
was difficult, as numerous Redis commands introduce nondeterministic
behavior.  Some of these are obvious (e.g., {\tt randomkey, srandmember}) by
name.  Given an understanding of Redis semantics, that the various
commands producing data with a limited lifetime (e.g., {\tt expire,
  pexpire}) also introduce timing-based nondeterminism is also clear.
However, that a command such as {\tt restore} takes an expiration
argument is not obvious on inspection, nor is the behavior of {\tt
  spop} which pops a random value from a set.  Moreover, it is
difficult to guess whetehr the {\tt pipe} mechanism, which allows a
large sequence of commands to be queued up in a pipe and executed all
at once, introduced the potential for nondeterminism (does it execute
sequentially before other command are handled, or is it in parallel
with further commands).  Deep experience with Redis would make these
issues clear, but tests using a library are often written by those not
intimately familliar with the semantics of every used library (otherwise they would not have
been as likely to introduce flaky tests in the first place).  This is
even more true in the case of automated test generation, where the
test engineer is often chosen for expertise in test generation tools,
not in the domain of the software under test (SUT), and is seldom the
original developer of the code.

>>>>

Using TSTL's harness for {\tt redis-py}, both {\tt redis-py} and Redis
itself can be tested; unfortunately, generating standalone
high-coverage regression tests for {\tt redis-py} and Redis using TSTL
has proven difficult, as numerous Redis commands introduce nondeterministic
behavior.   Using {\tt tstl\_afl\_fuzz}, we can see that the {\tt redis-py} has a 
stability of only 56.26\%, a clear indicator of nondeterminism. Some
of the problematic commands are obvious simply by inspection (e.g.,
{\tt randomkey, srandmember}).  And, given an understanding of Redis
semantics, it is also clear that the various
commands producing data with a limited lifetime (e.g., {\tt expire,
  pexpire}) also introduce timing-based nondeterminism.

However, that a command such as {\tt restore} takes an expiration
argument is not obvious to a non-expert, nor is the behavior of {\tt
  spop} which pops a random value from a set.  Moreover, it is
difficult to guess whetehr the {\tt pipe} mechanism, which allows a
large sequence of commands to be queued up in a pipe and executed all
at once, introduced the potential for nondeterminism (does it execute
sequentially before other command are handled, or is it in parallel
with further commands).  Deep experience with Redis would make these
issues clear, but tests using a library are often written by those not
intimately familliar with the semantics of every used library (otherwise they would not have
been as likely to introduce flaky tests in the first place).  This is
even more true in the case of automated test generation, where the
test engineer is often chosen for expertise in test generation tools,
not in the domain of the software under test (SUT), and is seldom the
original developer of the code.
